Tropical Andes frugivore trait data Frugivoria

### 2023-08-01 code/L0/L0_TropicalAndes_frugivores_frugivoria_traits.Rmd
correct species list to IUCN_species_name not species

```{r}
print("The number of records is")
nrow(Frugivoria)
print("The number of species is" )
length(unique(Frugivoria$species))
print("The number of families is" )
length(unique(Frugivoria$family))
```

# Extract species list
```{r}
Frugivoria_SpeciesList <- unique(Frugivoria$species)
```

>>>>

```{r}
print("The number of records is")
nrow(Frugivoria)
print("The number of species is" )
length(unique(Frugivoria$IUCN_species_name))
print("The number of families is" )
length(unique(Frugivoria$family))
```

# Extract species list
```{r}
Frugivoria_SpeciesList <- unique(Frugivoria$IUCN_species_name)
```
